---
title: "plotly"
author: "Sukhvir"
date: "August 21, 2020"
output:
  word_document: default
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

R Markdown & Plotly

```{r plotly}
library(plotly)
library(tidyr)
library(dplyr)
library(data.table)
dat <- data.table(mtcars, keep.rownames = TRUE)
dat[rn %like% "^M"]
```

## Distribution of Cars by Mileage

```{r}
library(ggplot2)
ggplot(mtcars, aes(mpg)) +
  geom_histogram(binwidth = 4) + xlab('Miles per Gallon') + ylab('Number of Cars') + 
   ggtitle('Distribution of Cars by Mileage')
```

## Distribution of Cars by Cylinders

```{r}
ggplot(mtcars, aes(cyl)) +
  geom_histogram(binwidth=1) + xlab('Cylinders') + ylab('Number of Cars') +
   ggtitle('Distribution of Cars by Cylinders')
```

## Distribution of Cars by Horsepower

```{r}
ggplot(mtcars, aes(hp)) +
  geom_histogram(binwidth=20) + xlab('horsepower') + ylab('Number of Cars') +
  ggtitle('Distribution of Cars by Horsepower')
```

## correlation of hp and mpg

```{r}
cor(mtcars$mpg, mtcars$hp)
```

## Plotting the data - HP vs MPG

```{r}
ggplot(mtcars, aes(hp, mpg)) + geom_point() +
  geom_smooth(method = "lm", se = FALSE) +
  ylab("Miles per Gallon") +
  xlab("No. of Horsepower") +
  ggtitle("Impact of Number of Horsepower on MPG")

```

## Impact of Number of Horsepower on MPG

```{r}
ggplot(mtcars, aes(hp, mpg)) +
  stat_smooth() + geom_point() +
  ylab("Miles per Gallon") +
  xlab ("No. of Horsepower") +
  ggtitle("Impact of Number of Horsepower on MPG")

```

## Impact of Number of Cylinders on MPG

```{r}
ggplot(mtcars, aes(cyl, mpg)) + geom_point() +
  geom_smooth(method = "lm", se = FALSE) +
  ylab("Miles per Gallon") + xlab("No. of Cylinders") +
  ggtitle("Impact of Number of Cylinders on MPG")
```

## Result
The analysis indicates a strong negative correlation for both number of horsepower (-0.77) as well as number of cylinders (-0.85) on miles per gallon.
